Technical Report

### 2017-11-15 fully-abstract-comp/technical-report.tex
Refined worlds and priv. future world relation

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\spatial}{\mathrm{spatial}}
\newcommand{\spatialo}{\mathrm{spatial\_owned}}
\newcommand{\pure}{\mathrm{pure}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\lau{06-11-2017: If we need to introduce revoked regions like we had for the local capabilities, we may consider the following: For the future world relation require the existence of a bijection from region names to region names. For all regions in the present world the future region is given by the bijection. This would mean that reinstantiation would happen simply by giving a bijection that maps to the new region. In other words, the weird shadowing would not be necessary.
  \begin{mathpar}
    \inferrule{ \dom(W') \supseteq \dom(W) \\ \exists m : \RegionName \fun \RegionName, \text{ $m$ injective} \ldotp \forall r \in \dom(W) \ldotp W'(m(r)) \pubft W(r) }
    { W' \pubft W }
  \end{mathpar}
}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\spatial \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\spatialo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\spatial$ and $\spatialo$ are regions governing segments of memory addressed by linear capabilities. $\spatialo$ signifies that this region is addressable. $\spatial$ signifies that the region is not owned and can thus not be addressed. Finally, $\pure$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitly into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

@@

>>>>

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\spatial}{\mathrm{spatial}}
\newcommand{\spatialo}{\mathrm{spatial\_owned}}
\newcommand{\pure}{\mathrm{pure}}
\newcommand{\revoked}{\mathrm{revoked}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\lau{06-11-2017: If we need to introduce revoked regions like we had for the local capabilities, we may consider the following: For the future world relation require the existence of a bijection from region names to region names. For all regions in the present world the future region is given by the bijection. This would mean that reinstantiation would happen simply by giving a bijection that maps to the new region. In other words, the weird shadowing would not be necessary.
  \begin{mathpar}
    \inferrule{ \dom(W') \supseteq \dom(W) \\ \exists m : \RegionName \fun \RegionName, \text{ $m$ injective} \ldotp \forall r \in \dom(W) \ldotp W'(m(r)) \pubft W(r) }
    { W' \pubft W }
  \end{mathpar}
}
\lau{10-11-2017: The above may not work well here because we do not want a $\spatialo$ region to be taken over by a $\pure$ region (as this would allow for normal capabilities addressing an area of memory that was only addressable by linear capabilities before).}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\spatial \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2}) \uplus \\
    \{\spatialo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\uplus \\
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2}) \uplus\\
    \{\revoked\}
  \end{array} \right.
\]
where $\spatial$ and $\spatialo$ are regions governing segments of memory addressed by linear capabilities. $\spatialo$ signifies that this region is addressable. $\spatial$ signifies that the region is not owned and can thus not be addressed. Finally, $\pure$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitly into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

@@

For both $\privft$ and $\pubft$ we have
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
            { W' \future W }
\end{mathpar}

The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
            { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi^\pub,\phi,H) \privft (v,s,\phi^\pub,\phi,H)  }

\end{mathpar}
